Crowdy: Social Crowd Visualization

### 2011-04-28 docs/crowdy_gui.tex
fixed pilot study

\section{Evaluation Plan}
In order to evaluate our system, we planned to conduct a 2-step usability study
which includes a pilot study, and an evaluation study. In the pilot study, we
will ask a relative small number of users (e.g., 5 - 10 people) to try our
system, and fill in the usability questionaire. Then, we will refine the system
based on the feedbacks from the pilot study (i.e., fixing bugs reported by users,
modifying featuers that were not preferred). Finally, a large scale evaluation
study also in the form of questionaire will be conducted on a user base of 30 -
50 users including three types of users we mentioned earlier: normal users, 
Twitter users, and analysts. The refinement step and the large-scale detailed
evaluation study will be generated after the step of the pilot study. Thus, in
this report, we only focus on the design of the pilot study.

@@

The pilot study we propose contains XX 5-scale likert (i.e., very good, good,
okay, bad, and very bad) questions, and YY open questions. The likert-scale questions
are listed below:

\begin{itemize}
\item Whether the interface for timeline view is easy to use?
\item Whether the interface for list view is easy to use?
\item Whether the search feature for timeline view is easy to use?
\item Whether the search feature for list view is easy to use?
\item Whether the search results in the timeline view could answer the information
need for your query.
\item Whether the search results in the list view could answer the information
need for your query.
\end{itemize}

Besides, here are the open questions:
\begin{itemize}
\item What are the features that you like most? Why?
\item What are the features that you don't like / hate most? Why?
\item What features that you would like Crowdy to implement in the future?
\item Any other comments? 
\end{itemize}

>>>>

\section{Evaluation Plan}
In order to evaluate our system, we plan to conduct a 2-step usability study
which includes a pilot study, and an evaluation study. In the pilot study, we
will ask a relative small number of users (e.g., 5 - 10 people) to try our
system, and fill in the usability questionaire. Then, we will refine the system
based on the feedbacks from the pilot study (i.e., fixing bugs reported by users,
modifying featuers that were not preferred). Finally, a large scale evaluation
study also in the form of questionaire will be conducted on a user base of 30 -
50 users including three types of users we mentioned earlier: normal users, 
Twitter users, and analysts. The refinement step and the large-scale detailed
evaluation study will be generated after the step of the pilot study. Thus, in
this report, we only focus on the design of the pilot study.

@@

The pilot study we propose contains basic demographic information, five questions with a
five point Likert scale (i.e., strongly agree, agree
neutral, disagree, and strongly disagree), and four open questions. The
Likert scale questions are listed below:

\begin{itemize}
\item The interface for timeline view is easy to use.
\item The interface for list view is easy to use.
\item The search feature for timeline view is easy to use.
\item The search feature for list view is easy to use.
\item I could use the search features to find crowds that I was interested in.
\end{itemize}

We would also ask some open-ended questions:
\begin{itemize}
\item What are the features that you like most? Why?
\item What are the features that you don't like / hate most? Why?
\item What features that you would like Crowdy to implement in the future?
\item Do you have any other comments? 
\end{itemize}

Once we have the results of the pilot study, we can refine the test procedures
and questionnaire. We will run this study on a larger group of poeple.
